\documentclass[../main.tex]{subfiles}
\begin{document}

\section{Survey Measurement Items}

This annex presents all measurement items used in the empirical survey, organized by theoretical construct. Each table displays the construct name, original items from the literature, adapted items for this study, scaling method, and source references. The items were measured using 5-point Likert scales (ranging from 1 = \textit{strongly disagree} to 5 = \textit{strongly agree}) unless otherwise noted. All items were presented to participants in German.

The constructs measured in this study include: Treatment Check, Perceived Usefulness (PUF), Ease of Use (EOU), Behavioral Intention (BI), Explainable AI Trust (XAIT), Familiarity with Technology (FAM-TEC), and Collaborative Intention (CI). These constructs form the theoretical foundation of the research model and were selected based on their relevance to understanding user acceptance and trust in AI systems.

\subsection{Treatment Check}
\label{subsec:treatment-check-items}
The treatment check item was used to verify that participants noticed the experimental manipulation regarding answer certainty/uncertainty indicators in the AI system responses.

\input{../../resources/tables/table_Treatment_Check.tex}

\subsection{Perceived Usefulness (PUF)}
\label{subsec:puf-items}
Perceived Usefulness measures the degree to which participants believe that using the AI system (Alva) would enhance their work performance and productivity.

\input{../../resources/tables/table_PUF.tex}

\subsection{Ease of Use (EOU)}
\label{subsec:eou-items}
Ease of Use assesses how effortlessly participants can interact with and utilize the AI system without requiring extensive cognitive effort.

\input{../../resources/tables/table_EOU.tex}

\subsection{Behavioral Intention (BI)}
\label{subsec:bi-items}
Behavioral Intention captures participants' willingness and intention to use AI systems in future contexts and applications.

\input{../../resources/tables/table_BI.tex}

\subsection{Explainable AI Trust (XAIT)}
\label{subsec:xait-items}
Explainable AI Trust measures participants' general attitudes toward AI, including trust, fear, and beliefs about AI's impact on society and employment.

\input{../../resources/tables/table_XAIT.tex}

\subsection{Familiarity with Technology (FAM-TEC)}
\label{subsec:fam-tec-items}
Familiarity with Technology assesses participants' prior knowledge and experience with generative AI systems such as ChatGPT, Copilot, or Gemini.

\input{../../resources/tables/table_FAM-TEC.tex}

\subsection{Collaborative Intention (CI)}
\label{subsec:ci-items}
Collaborative Intention evaluates participants' perceptions of the AI system's accuracy, dependability, consistency, and efficiency in collaborative interactions.

\input{../../resources/tables/table_CI.tex}

\end{document}
